Comparison of MCMC algorithms in Stochastic Volatility Models

### 2023-09-28 manuscript/main.tex
Extra histograms and ess plots

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_1k.png}
        \caption{Distribution of rank statistics for centered and non centered Hamiltoninan Monte Carlo (static parameters). Non centered histograms look approximately uniform. The centered parameterisation struggles to estimate $\sigma^2$}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/ksc_1k.png}
        \caption{Distribution of rank statistics for centered and non centered Gaussian mixture model(static parameters). All parameters display a lack of calibration}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/sir_1k.png}
        \caption{Distribution of rank statistics for weighted resampled model (static parameters) with 1000 SBC iterations. All parameters display a lack of calibration}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/sir_5k.png}
        \caption{Distribution of rank statistics for weighted resampled model (static parameters) with 5000 SBC iterations. Increasing number of SBC parameters does not improve results}
    \end{figure}

>>>>

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_1k.png}
        \caption{Distribution of 1000 rank statistics for centered and non centered Hamiltoninan Monte Carlo (static parameters). Non centered histograms look approximately uniform. The centered parameterisation struggles to estimate $\sigma^2$}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_5k.png}
        \caption{Distribution of 5000 rank statistics for centered and non centered Hamiltoninan Monte Carlo (static parameters). Non centered histograms look approximately uniform. The centered parameterisation struggles to estimate $\sigma^2$}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/hmc_ess.png}
        \caption{Boxplots of effective sample size after 5000 iterations of SBC}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/ksc_1k.png}
        \caption{Distribution of 1000 rank statistics for centered and non centered Gaussian mixture model(static parameters). All parameters display a lack of calibration}
    \end{figure}

@@

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/sir_1k.png}
        \caption{Distribution of 1000 rank statistics for weighted resampled model (static parameters) with 1000 SBC iterations. All parameters display a lack of calibration}
    \end{figure}

    \begin{figure}[H]
        \centering
        \includegraphics[scale=0.1]{results/sir_5k.png}
        \caption{Distribution of 5000 rank statistics for weighted resampled model (static parameters) with 5000 SBC iterations. Increasing number of SBC parameters does not improve results}
    \end{figure}
